以太坊：一种安全去中心化的通用交易账本 \\ {\smaller \textbf{EIP-150版本 (\YellowPaperVersionNumber{})}}

### 2017-08-13 Paper_Chinese.tex
翻译完 4.2 交易

\par
\begin{center}
\begin{tabular}{rl}
\toprule
倍数 & 面值 \\
\midrule
$10^0$ & Wei(伟)) \\
$10^{12}$ & Szabo(萨博) \\
$10^{15}$ & Finney(芬尼) \\
$10^{18}$ & Ether(以太) \\
\bottomrule
\end{tabular}
\end{center}
\par

@@

I use a number of typographical conventions for the formal notation, some of which are quite particular to the present work:

The two sets of highly structured, `top-level', state values, are denoted with bold lowercase Greek letters. They fall into those of world-state, which are denoted $\boldsymbol{\sigma}$ (or a variant thereupon) and those of machine-state, $\boldsymbol{\mu}$.

Functions operating on highly structured values are denoted with an upper-case greek letter, \eg $\Upsilon$, the Ethereum state transition function.

For most functions, an uppercase letter is used, e.g. $C$, the general cost function. These may be subscripted to denote specialised variants, \eg $C_\text{\tiny SSTORE}$, the cost function for the {\tiny SSTORE} operation. For specialised and possibly externally defined functions, I may format as typewriter text, \eg the Keccak-256 hash function (as per the winning entry to the SHA-3 contest) is denoted $\texttt{KEC}$ (and generally referred to as plain Keccak). Also $\texttt{KEC512}$ is referring to the Keccak 512 hash function.

Tuples are typically denoted with an upper-case letter, \eg $T$, is used to denote an Ethereum transaction. This symbol may, if accordingly defined, be subscripted to refer to an individual component, \eg $T_n$, denotes the nonce of said transaction. The form of the subscript is used to denote its type; \eg uppercase subscripts refer to tuples with subscriptable components.

Scalars and fixed-size byte sequences (or, synonymously, arrays) are denoted with a normal lower-case letter, \eg $n$ is used in the document to denote a transaction nonce. Those with a particularly special meaning may be greek, \eg $\delta$, the number of items required on the stack for a given operation.

Arbitrary-length sequences are typically denoted as a bold lower-case letter, \eg $\mathbf{o}$ is used to denote the byte sequence given as the output data of a message call. For particularly important values, a bold uppercase letter may be used.

Throughout, we assume scalars are positive integers and thus belong to the set $\mathbb{P}$. The set of all byte sequences is $\mathbb{B}$, formally defined in Appendix \ref{app:rlp}. If such a set of sequences is restricted to those of a particular length, it is denoted with a subscript, thus the set of all byte sequences of length $32$ is named $\mathbb{B}_{32}$ and the set of all positive integers smaller than $2^{256}$ is named $\mathbb{P}_{256}$. This is formally defined in section \ref{ch:block}.

Square brackets are used to index into and reference individual components or subsequences of sequences, \eg $\boldsymbol{\mu}_\mathbf{s}[0]$ denotes the first item on the machine's stack. For subsequences, ellipses are used to specify the intended range, to include elements at both limits, \eg $\boldsymbol{\mu}_\mathbf{m}[0..31]$ denotes the first 32 items of the machine's memory.

In the case of the global state $\boldsymbol{\sigma}$, which is a sequence of accounts, themselves tuples, the square brackets are used to reference an individual account.

When considering variants of existing values, I follow the rule that within a given scope for definition, if we assume that the unmodified `input' value be denoted by the placeholder $\Box$ then the modified and utilisable value is denoted as $\Box'$, and intermediate values would be $\Box^*$,  $\Box^{**}$ \&c. On very particular occasions, in order to maximise readability and only if unambiguous in meaning, I may use alpha-numeric subscripts to denote intermediate values, especially those of particular note.

When considering the use of existing functions, given a function $f$, the function $f^*$ denotes a similar, element-wise version of the function mapping instead between sequences. It is formally defined in section \ref{ch:block}.

I define a number of useful functions throughout. One of the more common is $\ell$, which evaluates to the last item in the given sequence:

@@

\section{Blocks, State and Transactions} \label{ch:bst}

Having introduced the basic concepts behind Ethereum, we will discuss the meaning of a transaction, a block and the state in more detail.

\subsection{World State} \label{ch:state}

The world state (\textit{state}), is a mapping between addresses (160-bit identifiers) and account states (a data structure serialised as RLP, see Appendix \ref{app:rlp}). Though not stored on the blockchain, it is assumed that the implementation will maintain this mapping in a modified Merkle Patricia tree (\textit{trie}, see Appendix \ref{app:trie}). The trie requires a simple database backend that maintains a mapping of bytearrays to bytearrays; we name this underlying database the state database. This has a number of benefits; firstly the root node of this structure is cryptographically dependent on all internal data and as such its hash can be used as a secure identity for the entire system state. Secondly, being an immutable data structure, it allows any previous state (whose root hash is known) to be recalled by simply altering the root hash accordingly. Since we store all such root hashes in the blockchain, we are able to trivially revert to old states.

The account state comprises the following four fields:

\begin{description}
\item[nonce] A scalar value equal to the number of transactions sent from this address or, in the case of accounts with associated code, the number of contract-creations made by this account. For account of address $a$ in state $\boldsymbol{\sigma}$, this would be formally denoted $\boldsymbol{\sigma}[a]_n$.
\item[balance] A scalar value equal to the number of Wei owned by this address. Formally denoted $\boldsymbol{\sigma}[a]_b$.
\item[storageRoot] A 256-bit hash of the root node of a Merkle Patricia tree that encodes the storage contents of the account (a mapping between 256-bit integer values), encoded into the trie as a mapping from the Keccak 256-bit hash of the  256-bit integer keys to the RLP-encoded 256-bit integer values. The hash is formally denoted $\boldsymbol{\sigma}[a]_s$.
\item[codeHash] The hash of the EVM code of this account---this is the code that gets executed should this address receive a message call; it is immutable and thus, unlike all other fields, cannot be changed after construction. All such code fragments are contained in the state database under their corresponding hashes for later retrieval. This hash is formally denoted $\boldsymbol{\sigma}[a]_c$, and thus the code may be denoted as $\mathbf{b}$, given that $\texttt{\small KEC}(\mathbf{b}) = \boldsymbol{\sigma}[a]_c$.
\end{description}

Since I typically wish to refer not to the trie's root hash but to the underlying set of key/value pairs stored within, I define a convenient equivalence:
\begin{equation}
\texttt{\small TRIE}\big(L_I^*(\boldsymbol{\sigma}[a]_\mathbf{s})\big) \equiv \boldsymbol{\sigma}[a]_s
\end{equation}

The collapse function for the set of key/value pairs in the trie, $L_I^*$, is defined as the element-wise transformation of the base function $L_I$, given as:
\begin{equation}
L_I\big( (k, v) \big) \equiv \big(\texttt{\small KEC}(k), \texttt{\small RLP}(v)\big)
\end{equation}

where:
\begin{equation}
k \in \mathbb{B}_{32} \quad \wedge \quad v \in \mathbb{P}
\end{equation}

It shall be understood that $\boldsymbol{\sigma}[a]_\mathbf{s}$ is not a `physical' member of the account and does not contribute to its later serialisation.

If the \textbf{codeHash} field is the Keccak-256 hash of the empty string, i.e. $\boldsymbol{\sigma}[a]_c = \texttt{\small KEC}\big(()\big)$, then the node represents a simple account, sometimes referred to as a ``non-contract'' account.

Thus we may define a world-state collapse function $L_S$:
\begin{equation}
L_S(\boldsymbol{\sigma}) \equiv \{ p(a): \boldsymbol{\sigma}[a] \neq \varnothing \}
\end{equation}
where
\begin{equation}
p(a) \equiv  \big(\texttt{\small KEC}(a), \texttt{\small RLP}\big( (\boldsymbol{\sigma}[a]_n, \boldsymbol{\sigma}[a]_b, \boldsymbol{\sigma}[a]_s, \boldsymbol{\sigma}[a]_c) \big) \big)
\end{equation}

This function, $L_S$, is used alongside the trie function to provide a short identity (hash) of the world state. We assume:
\begin{equation}
\forall a: \boldsymbol{\sigma}[a] = \varnothing \; \vee \; (a \in \mathbb{B}_{20} \; \wedge \; v(\boldsymbol{\sigma}[a]))
\end{equation}
where $v$ is the account validity function:
\begin{equation}
\quad v(x) \equiv x_n \in \mathbb{P}_{256} \wedge x_b \in \mathbb{P}_{256} \wedge x_s \in \mathbb{B}_{32} \wedge x_c \in \mathbb{B}_{32}
\end{equation}

\subsection{The Transaction} \label{ch:transaction}

A transaction (formally, $T$) is a single cryptographically-signed instruction constructed by an actor externally to the scope of Ethereum. While it is assumed that the ultimate external actor will be human in nature, software tools will be used in its construction and dissemination\footnote{Notably, such `tools' could ultimately become so causally removed from their human-based initiation---or humans may become so causally-neutral---that there could be a point at which they rightly be considered autonomous agents. \eg contracts may offer bounties to humans for being sent transactions to initiate their execution.}. There are two types of transactions: those which result in message calls and those which result in the creation of new accounts with associated code (known informally as `contract creation'). Both types specify a number of common fields:

\begin{description}
\item[nonce] A scalar value equal to the number of transactions sent by the sender; formally $T_n$.
\item[gasPrice] A scalar value equal to the number of Wei to be paid per unit of \textit{gas} for all computation costs incurred as a result of the execution of this transaction; formally $T_p$.
\item[gasLimit] A scalar value equal to the maximum amount of gas that should be used in executing this transaction. This is paid up-front, before any computation is done and may not be increased later; formally $T_g$.
\item[to] The 160-bit address of the message call's recipient or, for a contract creation transaction, $\varnothing$, used here to denote the only member of $\mathbb{B}_0$ ; formally $T_t$.
\item[value] A scalar value equal to the number of Wei to be transferred to the message call's recipient or, in the case of contract creation, as an endowment to the newly created account; formally $T_v$.
\item[v, r, s] Values corresponding to the signature of the transaction and used to determine the sender of the transaction; formally $T_w$, $T_r$ and $T_s$. This is expanded in Appendix \ref{app:signing}.
\end{description}

Additionally, a contract creation transaction contains:

\begin{description}
\item[init] An unlimited size byte array specifying the EVM-code for the account initialisation procedure, formally $T_\mathbf{i}$.
\end{description}

\textbf{init} is an EVM-code fragment; it returns the \textbf{body}, a second fragment of code that executes each time the account receives a message call (either through a transaction or due to the internal execution of code). \textbf{init} is executed only once at account creation and gets discarded immediately thereafter.

In contrast, a message call transaction contains:

\begin{description}
\item[data] An unlimited size byte array specifying the input data of the message call, formally $T_\mathbf{d}$.
\end{description}

Appendix \ref{app:signing} specifies the function, $S$, which maps transactions to the sender, and happens through the ECDSA of the SECP-256k1 curve, using the hash of the transaction (excepting the latter three signature fields) as the datum to sign. For the present we simply assert that the sender of a given transaction $T$ can be represented with $S(T)$.

@@

Here, we assume all components are interpreted by the RLP as integer values, with the exception of the arbitrary length byte arrays $T_\mathbf{i}$ and $T_\mathbf{d}$.
\begin{equation}
\begin{array}[t]{lclclc}
T_n \in \mathbb{P}_{256} & \wedge & T_v \in \mathbb{P}_{256} & \wedge & T_p \in \mathbb{P}_{256} & \wedge \\
T_g \in \mathbb{P}_{256} & \wedge & T_w \in \mathbb{P}_5 & \wedge & T_r \in \mathbb{P}_{256} & \wedge \\
T_s \in \mathbb{P}_{256} & \wedge & T_\mathbf{d} \in \mathbb{B} & \wedge & T_\mathbf{i} \in \mathbb{B}
\end{array}
\end{equation}
where
\begin{equation}
\mathbb{P}_n = \{ P: P \in \mathbb{P} \wedge P < 2^n \}
\end{equation}

The address hash $T_\mathbf{t}$ is slightly different: it is either a 20-byte address hash or, in the case of being a contract-creation transaction (and thus formally equal to $\varnothing$), it is the RLP empty byte sequence and thus the member of $\mathbb{B}_0$:
\begin{equation}
T_\mathbf{t} \in \begin{cases} \mathbb{B}_{20} & \text{if} \quad T_t \neq \varnothing \\
\mathbb{B}_{0} & \text{otherwise}\end{cases}
\end{equation}

\subsection{The Block} \label{ch:block}

The block in Ethereum is the collection of relevant pieces of information (known as the block \textit{header}), $H$, together with information corresponding to the comprised transactions, $\mathbf{T}$, and a set of other block headers $\mathbf{U}$ that are known to have a parent equal to the present block's parent's parent (such blocks are known as \textit{ommers}\footnote{\textit{ommer} is the most prevalent (not saying much) gender-neutral term to mean ``sibling of parent''; see \url{http://nonbinary.org/wiki/Gender_neutral_language#Family_Terms}}). The block header contains several pieces of information:

%\textit{TODO: Introduce logs}

\begin{description}
\item[parentHash] The Keccak 256-bit hash of the parent block's header, in its entirety; formally $H_p$.
\item[ommersHash] The Keccak 256-bit hash of the ommers list portion of this block; formally $H_o$.
\item[beneficiary] The 160-bit address to which all fees collected from the successful mining of this block be transferred; formally $H_c$.
\item[stateRoot] The Keccak 256-bit hash of the root node of the state trie, after all transactions are executed and finalisations applied; formally $H_r$.
\item[transactionsRoot] The Keccak 256-bit hash of the root node of the trie structure populated with each transaction in the transactions list portion of the block; formally $H_t$.
\item[receiptsRoot] The Keccak 256-bit hash of the root node of the trie structure populated with the receipts of each transaction in the transactions list portion of the block; formally $H_e$.
\item[logsBloom] The Bloom filter composed from indexable information (logger address and log topics) contained in each log entry from the receipt of each transaction in the transactions list; formally $H_b$.
\item[difficulty] A scalar value corresponding to the difficulty level of this block. This can be calculated from the previous block's difficulty level and the timestamp; formally $H_d$.
\item[number] A scalar value equal to the number of ancestor blocks. The genesis block has a number of zero; formally $H_i$.
\item[gasLimit] A scalar value equal to the current limit of gas expenditure per block; formally $H_l$.
\item[gasUsed] A scalar value equal to the total gas used in transactions in this block; formally $H_g$.
\item[timestamp] A scalar value equal to the reasonable output of Unix's time() at this block's inception; formally $H_s$.
\item[extraData] An arbitrary byte array containing data relevant to this block. This must be 32 bytes or fewer; formally $H_x$.
\item[mixHash] A 256-bit hash which proves combined with the nonce that a sufficient amount of computation has been carried out on this block; formally $H_m$.
\item[nonce] A 64-bit hash which proves combined with the mix-hash that a sufficient amount of computation has been carried out on this block; formally $H_n$.
\end{description}

The other two components in the block are simply a list of ommer block headers (of the same format as above) and a series of the transactions. Formally, we can refer to a block $B$:
\begin{equation}
B \equiv (B_H, B_\mathbf{T}, B_\mathbf{U})
\end{equation}

\subsubsection{Transaction Receipt}

>>>>

\par
\begin{center}
\begin{tabular}{rl}
\toprule
倍数 & 面值 \\
\midrule
$10^0$ & Wei(伟) \\
$10^{12}$ & Szabo(萨博) \\
$10^{15}$ & Finney(芬尼) \\
$10^{18}$ & Ether(以太) \\
\bottomrule
\end{tabular}
\end{center}
\par

@@

我用了大量的印刷约定表示公式中的符号，其中一些需要特别说明：

有两个高度结构化的顶层状态值,使用粗体小写希腊字母: $\boldsymbol{\sigma}$  表示世界状态(world-state);  $\boldsymbol{\mu}$ 表示机器状态（machine-state）。

作用在高度结构化值上的函数，使用大写的希腊字母，例如： $\Upsilon$ , 是以太坊中的状态转换函数。

对于大部分函数来说，通常用一个大写的字母表示，例如：$C$, 表示费用函数。可能会使用下角标表示为一些特别的变量，例如：$C_\text{\tiny SSTORE}$，表示执行 {\tiny SSTORE} 操作的费用函数。对于一些可能是外部定义的函数，可能会使用打印机文字字体，例如：$\texttt{KEC512}$ 哈希函数（为赢得进入SHA-3竞赛） ,使用 $\texttt{KEC}$ 表示。$\texttt{KEC512}$  表示 Keccack-512 哈希函数。

元组通常使用一个大写字母，例如：$T$，表示一个以太坊交易。使用下标可能会表示一个独立的变量,例如： $T_n$ ，表示交易中随机数。角标的形式用于表示它们的类型；例如：大写的下角标表示元组包含的下角标变量。

标量和固定大小的字节序列（或数组）都使用小写字母来表示，例如： $n$ 在本文中表示交易随机数。小写的希腊字母一般表示一些特别的含义，例如：$\delta$ 表示在栈上一个给定操作需要的条目数量。

任意长度的序列通常用加粗的小写字母表示，例如 $\mathbf{o}$ 表示消息调用中输出的数据字节序列。有时候，会对特别重要的值使用粗体。

我们认为标量都是正整数且属于集合 $\mathbb{P}$。所有的字节序列属于集合 $\mathbb{B}$，附录 \ref{app:rlp} 给出了正式的定义。用下角标符号表示这样的序列集合限制在一定长度以内, 长度为32的字节序列使用 $\mathbb{B}_{32}$ 表示, 所有比 $2^{256}$ 小的正整数使用 $\mathbb{P}_{256}$ 表示。详细定义见 \ref{ch:block}。

使用方括号表示序列中的一个元素或子序列,例如： $\boldsymbol{\mu}_\mathbf{s}[0]$ 表示计算机堆栈中的第一个条目。对于子序列来说，使用省略号表示一定的范围，且含头尾的限制，例如：$\boldsymbol{\mu}_\mathbf{m}[0..31]$ 表示计算机内存中的前32个条目。

在全局状态的情况下，σ是一个含多个账号的序列，本身的数组，正方形括号被用作去表示一个单独的账号。

以全局状态 $\boldsymbol{\sigma}$ 为例, 它表示一系列的账户, 它们自身的元组, 方括号用于表示一个独立的账户。

当去考虑现有的变量时，我遵循在给定的范围内去定义的原则，我们使用占位符 $\Box$ 表示未修改的输入变量, 使用 $\Box'$ 表示修改的和可用的变量, $\Box^*$,  $\Box^{**}$ \&c 表示中间变量。在特殊情况下，为了提高可读性和清晰性，我可能会使用字母-数字下角标表示中间值。

当使用去已有的函数时，给定一个函数 $f$,那么函数 $f^*$ 表示一个相似的、替换序列的函数映射。详细的定义见 \ref{ch:block}。

整个过程中，我定义了大量的函数。一个常见的函数是 $\ell$，表示给定序列的最后一个条目：

@@

\section{块、状态和交易} \label{ch:bst}

介绍了以太坊的基本概念后,我们将更详细地讨论交易、区块和状态的含义

\subsection{世界状态} \label{ch:state}

世界状态是在地址（160位的标志符）和账户状态（序列化为RLP的数据结构，详见附录 \ref{app:rlp}）的映射。虽然世界状态没有直接储存在区块链上，但会假定实施过程中会将这个映射维护在一个修改过的Merkle Patricia 树(简称trie，详见附录 \ref{app:trie}）。trie 需要一个简单的后端数据库去维护字节数组到字节数组的映射；我们称这个后端数据库为状态数据库。它有一系列的好处: 第一这个结构的根节点是加密的且依赖于所有的内部数据，且它的哈希可以作为整个系统状态的一个安全标志;第二，作为一个不变的数据结构，因此它允许任何一个之前状态（根部哈希已知的条件下）通过简单地改变根部哈希值而被召回。因为我们在区块链中储存了所以这样的根部哈希值，所以我们能恢复到指定的历史状态。

账户状态包含以下四个字段：
\begin{description}
\item[nonce,随机数] 这个值等于账户发出的交易数及这个账户创建的合约数量之和。 $\boldsymbol{\sigma}[a]_n$ 表示状态 $\boldsymbol{\sigma}$ 中的地址 $a$ 的nonce值。
\item[balance,余额] $\boldsymbol{\sigma}[a]_b$, 表示这个账户拥有多少Wei。
\item[storageRoot,存储跟节点] 保存账户内容的 Merkle Patricia 树根节点的256位哈希编码到trie中, 作为从 256位整数键值哈希的Keccak 256 位哈希到 256位整数的RLP-编码映射。这个哈希定义为 $\boldsymbol{\sigma}[a]_s$。
\item[codeHash,代码哈希] 这个账户的EVM(Ethereum Virtual Machine,以太坊虚拟机)代码的哈希值---代码执行时,这个地址会接收一个消息调用; 它和其它字段不同, 创建后不可更改。状态数据库中包含所有像这样的代码片段的哈希, 以便后续使用。 这个哈希定义为 $\boldsymbol{\sigma}[a]_c$,$\mathbf{b}$ 表示代码,  $\texttt{\small KEC}(\mathbf{b}) = \boldsymbol{\sigma}[a]_c$.
\end{description}

因为我通常希望所指的并不是trie树的根哈希,而是所保存的键值对集合，我做了一个更方便的定义:

\begin{equation}
\texttt{\small TRIE}\big(L_I^*(\boldsymbol{\sigma}[a]_\mathbf{s})\big) \equiv \boldsymbol{\sigma}[a]_s
\end{equation}

trie树中的键值对集合函数, $L_I^*$, 定义为基于基础函数 $L_I$ 的元素转换:
\begin{equation}
L_I\big( (k, v) \big) \equiv \big(\texttt{\small KEC}(k), \texttt{\small RLP}(v)\big)
\end{equation}

其中:
\begin{equation}
k \in \mathbb{B}_{32} \quad \wedge \quad v \in \mathbb{P}
\end{equation}

需要说明的是,$\boldsymbol{\sigma}[a]_\mathbf{s}$ 不应算作这个账户的"物理"成员, 它不参与序列化。

如果 \textbf{codeHash} 字段是一个空字符串的 Keccak-256 哈希, 例如 $\boldsymbol{\sigma}[a]_c = \texttt{\small KEC}\big(()\big)$, 则表示对应的节点表示一个简单账户, 有时简称"非合约"账户。

因此我们可能定义一个世界状态的函数  $L_S$：

\begin{equation}
L_S(\boldsymbol{\sigma}) \equiv \{ p(a): \boldsymbol{\sigma}[a] \neq \varnothing \}
\end{equation}
where
\begin{equation}
p(a) \equiv  \big(\texttt{\small KEC}(a), \texttt{\small RLP}\big( (\boldsymbol{\sigma}[a]_n, \boldsymbol{\sigma}[a]_b, \boldsymbol{\sigma}[a]_s, \boldsymbol{\sigma}[a]_c) \big) \big)
\end{equation}

函数 $L_S$ 和 trie 函数是为了提供一个世界状态的简短身份（哈希）。我们假定：
\begin{equation}
\forall a: \boldsymbol{\sigma}[a] = \varnothing \; \vee \; (a \in \mathbb{B}_{20} \; \wedge \; v(\boldsymbol{\sigma}[a]))
\end{equation}

$v$ 是账户合法性验证函数:
\begin{equation}
\quad v(x) \equiv x_n \in \mathbb{P}_{256} \wedge x_b \in \mathbb{P}_{256} \wedge x_s \in \mathbb{B}_{32} \wedge x_c \in \mathbb{B}_{32}
\end{equation}

\subsection{交易} \label{ch:transaction}

交易（符号，$T$）是个单一的加密指令，通过以太坊中系统之外的操作者创建。我们假设外部的操作者是人,软件工具用于创建和传播\footnote{显著地，这样的“工具”可以从基于人类行为的初始化中移除---或者人类可能变成有原因的中立---可能有一点他们被视为自治的代理人。例如：合约可能会给人类好处,让人发送交易从而触发合约的执行。}。这里的交易类型有两种：一种是消息调用,另一种通过代码创建新的账户（称为“合约创建”）。两种类型的交易都有的共同字段如下:

\begin{description}
\item[nonce,随机数] $T_n$,账户发出的交易数量。
\item[gasPrice,燃料价格] $T_p$, 为执行交易所需要的计算资源付的 \textit{gas} 价格, 以Wei为单位。
\item[gasLimit,燃料上限] $T_g$, 用于执行交易的最大 gas 数量。 这个值须在交易前设置,且设定后不能再修改。
\item[to, 接收者地址] 消息调用接收者的160位的地址。对与合约创建交易, 无需接收者地址, 使用 $\varnothing$ 表示, $\varnothing$ 是 $\mathbb{B}_0$ 的唯一成员。
\item[value, 转账额度] $T_v$, 转到接收者账户的额度,以Wei为单位。对于合约创建,表示捐赠到合约地址的额度。
\item[v, r, s] $T_w$, $T_r$ and $T_s$,和交易签名相关的变量, 用于确定交易的发送者。详见附录 \ref{app:signing}。
\end{description}

此外, 合约创建还包含以下字段:

\begin{description}
\item[init,初始化] $T_\mathbf{i}$, 一个不限制大小的字节数组,表示账户初始化程序的EVM代码。
\end{description}

\textbf{init} 是EVM代码片段; 执行 init后会返回另外一个代码片段, 每次合约接受消息调用(通过交易或内部调用)后都会执行这个代码片段。\textbf{init} 仅当合约账户创建的时候执行一次。

相比之下, 一个消息调用的交易包括:

\begin{description}
\item[data,数据] $T_\mathbf{d}$, 一个不限制大小的字节数组, 表示消息调用的输入数据。
\end{description}

附录 \ref{app:signing} 详细描述了映射发送者交易的函数 $S$, 通过 SECP-256k1 的 ECDSA 曲线, 使用交易(除了最后的3个签名字段)作为数据来签名。目前我们先简单使用 $S(T)$ 表示发送者的指定交易 $T$ 。

@@

在这里,我们假设所有变量都是 RLP 编码的整数, 除了2个任意长度的字节数组 $T_\mathbf{i}$ 和 $T_\mathbf{d}$。

\begin{equation}
\begin{array}[t]{lclclc}
T_n \in \mathbb{P}_{256} & \wedge & T_v \in \mathbb{P}_{256} & \wedge & T_p \in \mathbb{P}_{256} & \wedge \\
T_g \in \mathbb{P}_{256} & \wedge & T_w \in \mathbb{P}_5 & \wedge & T_r \in \mathbb{P}_{256} & \wedge \\
T_s \in \mathbb{P}_{256} & \wedge & T_\mathbf{d} \in \mathbb{B} & \wedge & T_\mathbf{i} \in \mathbb{B}
\end{array}
\end{equation}
其中
\begin{equation}
\mathbb{P}_n = \{ P: P \in \mathbb{P} \wedge P < 2^n \}
\end{equation}

地址哈希 $T_\mathbf{t}$ 稍微有些不同:它是一个20字节的地址哈希值, 但创建合约时它是RLP空字节系列, 表示为$\mathbb{B}_0$：
\begin{equation}
T_\mathbf{t} \in \begin{cases} \mathbb{B}_{20} & \text{if} \quad T_t \neq \varnothing \\
\mathbb{B}_{0} & \text{otherwise}\end{cases}
\end{equation}

\subsection{区块} \label{ch:block}

在以太坊中, 区块是相关信息的集合。区块头 $H$, 与之想对应的交易信息 $\mathbf{T}$, 其它区块头数据的集合 $\mathbf{U}$，$\mathbf{U}$ 表示它的父级区块中有和当前区块的爷爷辈区块是相同的。（这样的区块称为\textit{ommers}\footnote{\textit{ommer} 的意思和自然界中的 "父母的兄弟姐妹"最相近, 详见 \url{http://nonbinary.org/wiki/Gender_neutral_language#Family_Terms}}, 译者注:不妨称之为叔链)。区块头包含的的信息如下：

\begin{description}
\item[parentHash, 父块哈希] $H_p$,父区块头的 Keccak 256位哈希。
\item[ommersHash, 叔链哈希] $H_o$,当前区块的叔链列表 Keccak 256位哈希。
\item[beneficiary, 受益者地址] $H_c$, 成功挖到这个区块的160位地址, 这个区块中的所有交易费用都会转到这个地址。
\item[stateRoot,状态字典树根节点哈希] 状态字典树根节点的 Keccak 256位哈希, 交易打包到当前区块且区块定稿后可以生成这个值。
\item[transactionsRoot,交易字典树根节点哈希] 交易字典树根节点的 Keccak 256位哈希,在交易字典树含有区块中的所有交易列表。
\item[receiptsRoot,接受者字典树根节点哈希] 接受者字典树根节点的 Keccak 256位哈希,在接受者字典树含有区块中的所有交易信息中的接受者。
\item[logsBloom,日志Bloom] $H_b$, 日记Bloom过滤器由可索引信息（日志地址和日志主题）组成，这个信息包含在每个日志入口, 来自交易列表中的每个交易的接受者。
\item[difficulty,难度] $H_d$,表示当前区块的难度水平, 这个值根据前一个区块的难度水平和时间戳计算得到。
\item[number,区块编号] $H_i$,等于当前区块的直系前辈区块数量。 创始区块的区块编号为 0。
\item[gasLimit,燃料限制] $H_l$,目前每个区块的燃料消耗上限。
\item[gasUsed, 燃料使用量] $H_g$,当前区块的所有交易使用燃料之和。
\item[timestamp,时间戳] $H_s$,当前区块初始化时的Unix时间戳。
\item[extraData,附加数据] $H_x$, 32字节以内的字节数组。
\item[mixHash,混合哈希] $H_m$,与一个与随机数(nonce)相关的256位哈希计算, 用于证明针对当前区块已经完成了足够的计算。
\item[nonce,随机数] $H_n$, 一个 64 位哈希, 和计算混合哈希相关, 用于证明针对当前区块已经完成了足够的计算。
\end{description}

此外,当前区块还记录着这个区块的交易列表,以及2个叔链(ommer)的区块头列表。我们以 $B$ 表示一个区块:
\begin{equation}
B \equiv (B_H, B_\mathbf{T}, B_\mathbf{U})
\end{equation}

\subsubsection{交易收据}
